---
title: "Master Dataset"
author: "Erin Johnston"
date: "11/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

So far I have worked on two separate datasets for CPUE and BPUE. Adding 0's into the drift in which we didn't catch something of a particular species. I am now going to work on making a master dataset with 0's that I can use as the base for both CPUE and BPUE going forward. I will also consider adding MOCI data to this master dataset

```{r libraries, warning=F, message=F }

library(tidyverse)
library(here)

```

It will start off with the same raw data as I used in 01_DATA_cpue-add-zeros.Rmd

```{r raw data and initial clean}

CP_MLML_to_2019 <- read_csv(here("Data", "CP_MLML_to_2019.csv"))

## figure out which data are not there
CP_MLML_to_2019 %>%
  select(everything())%>%
  summarise_all(funs(sum(is.na(.))))

## drop the lines with no length or angler hours
CP_MLML_to_2019 <- CP_MLML_to_2019 %>%
  drop_na() ##124013

## arranging by catch frequency
numbers_caught <- plyr::count(CP_MLML_to_2019$species)%>%
  arrange(desc(freq))

## run to filter for 21 most common species
## justify this with % of data these spp make up
CP_MLML_to_2019 <- CP_MLML_to_2019 %>%
  filter(species %in% c("BLU", "GPR", "BLA", "OLV", "LCD", "VER", "DEA", "YTL",
                        "KLP", "CPR", "CNY", "CHN", "RSY", "BWN", "KGL", "QBK", 
                        "CBZ", "BAY", "PSD", "TRE", "SRY")) #123500

```


```{r}
## combining drift ID and size separated by underscore
CP_MLML_to_2019$drift_size <- paste(CP_MLML_to_2019$drift, CP_MLML_to_2019$length, sep = "_")

## nearly the same code as before, but with drift_size and species counted instead of drift and species counted. This will allow us to keep length inside the dataset.
## this is the code that will also add in 0's to drifts where there are no fishes caught of a particular species
## takes a while to run because it is making this wide and then long
CP_ML_count_drift_size_species <- CP_MLML_to_2019 %>%
  count(drift_size, species)%>%
  rename(numbercaught = n)%>%
  pivot_wider(names_from = drift_size,
              values_from = numbercaught)%>%
  pivot_longer(-species,
               names_to = "drift_size",
               values_to = "numbercaught") %>%
   mutate(numbercaught=case_when(
    is.na(numbercaught)~0,
    TRUE~ as.numeric(numbercaught)
  ))


metadata_CP_ML <- CP_MLML_to_2019 %>% 
  select(group, trip, area, site, month, day, year, gridcell, anglerhours, drift,
         drift_size)%>%
  distinct()

cpue_cp_ml <- left_join(CP_ML_count_drift_size_species, metadata_CP_ML, 
                        by = "drift_size") %>%
  mutate(cpue = numbercaught/anglerhours)%>%
  separate(drift_size, into = c("drift", "length"), sep = "_") %>%
  rename(site_1 = site)%>%
  transform(site_2 = substr(drift, 3, 3))%>%
  mutate(
    site = case_when(
      site_2 == "M" ~ "MPA",
      site_2 == "R" ~ "REF"))%>%
  select(-site_1, - site_2)

##qaqc ben 11-4-2020
## unique lengths

length(unique(cpue_cp_ml$length))*
#length(unique(cpue_cp_ml$species))*
length(unique(cpue_cp_ml$drift))


98*61*5259


length(unique(CP_ML_count_drift_size_species$drift_size))*
length(unique(CP_ML_count_drift_size_species$species))


```

# CPUE
Using the master data, how to calculate and subset out different parts of the data. CPUE for individual drift, with the metadata, CPUE by gridcell in each year is here also.

```{r various cpue code}

## this is how to get CPUE for each drift
atmp <- cpue_cp_ml %>%
  group_by(species, drift) %>%
  summarise(cpue_sum = sum(cpue))%>%
  filter(species == "BLU")

## what to include to get CPUE by drift with all other metadata included
atmp_2 <- cpue_cp_ml %>%
  group_by(species, drift, group, trip, area, site, month, day, year, gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))%>%
  filter(species == "BLU")

## unique(atmp_2$gridcell) 139 unique grid cell

atmp_3 <- cpue_cp_ml %>%
  group_by(species, gridcell) %>%
  summarise(cpue_sum = sum(cpue))%>%
  filter(species == "BLU")

## what to include to get CPUE by gridcell by year
atmp_4 <- cpue_cp_ml %>%
  group_by(species, group, area, site, year, gridcell) %>%
  summarise(cpue_sum = sum(cpue))%>%
  filter(species == "BLU")

```


Need unique combinations of all drifts and all sizes

```{r}

drifts_unique <- unique(CP_MLML_to_2019$drift)
lengths_unique <- unique(CP_MLML_to_2019$length)
species_unique <- unique(CP_MLML_to_2019$species)
#nope
#drifts_lengths_unique <- paste(drifts_unique, lengths_unique, sep = "_")

## made new dataframe with unique drift + lengths + species
drift_len_spec_df<- crossing(drifts_unique, lengths_unique, species_unique)


## make new column with drift_length_species
drift_len_spec_df$drift_len_spec <- paste(drift_len_spec_df$drifts_unique, drift_len_spec_df$lengths_unique, drift_len_spec_df$species_unique, sep = "_")


## makes new column with species and sizes in df appended  
CP_MLML_to_2019$species_size <- paste(CP_MLML_to_2019$species, CP_MLML_to_2019$length, sep = "_")

## makes new column with drift specie and lengths appended
CP_MLML_to_2019$drift_len_spec <- paste(CP_MLML_to_2019$drift, CP_MLML_to_2019$species_size, sep = "_")

## how many unique combos of species and size there are
cp_ml_species_size <- unique(CP_MLML_to_2019$species_size)
 
## new df with unique drifts and species_sizes 
drifts_species_lengths_unique <- crossing(drifts_unique, cp_ml_species_size)

## new column with drift speies and size
drifts_species_lengths_unique$drift_len_spec <- paste(drifts_species_lengths_unique$drifts_unique, drifts_species_lengths_unique$cp_ml_species_size, sep = "_")

CP_MLML_to_2019_comb <- left_join(drifts_species_lengths_unique, CP_MLML_to_2019 , by = "drift_species_lengths")

test_qc <- anti_join(CP_MLML_to_2019_comb, drifts_species_lengths_unique, by = "drift_species_lengths")
```


```{r}

## df with min and max length for 21 common species
possible_sizes <- CP_MLML_to_2019 %>%
  group_by(species) %>%
  summarise(min_len = min(length),
            max_len = max(length)) 

#ok this works, putting in body of loop
#blacks <- seq(13, 50, by = 1)
#try <- seq(possible_sizes$min_len, possible_sizes$max_len, by = 1)


## for loop set-up
## vector with all species
spec_vec <- unique(possible_sizes$species)


## blank dataframe
possible_spec_size <- data.frame(species = character(),
                      len = character())

## for loop to get all sizes between min and max length
for(i in spec_vec){
  pos_len <- possible_sizes %>%
    filter(species == i)
  all_len <- seq(pos_len$min_len, pos_len$max_len, by = 1)
  for(j in 1:length(all_len)){
    possible_spec_size <- bind_rows(possible_spec_size, c(species = i, 
                                                          len = all_len[j]))
  }
}

possible_spec_size$spec_size <- paste(possible_spec_size$species,
                                      possible_spec_size$len, sep = "_")

##copied from prev chunk
##5252 unique drifts
drifts_unique <- unique(CP_MLML_to_2019$drift)

spp_size_unique <- unique(CP_MLML_to_2019$species_size)


drift_spec_size_join <- crossing(drifts_unique, possible_spec_size)



drift_spec_size_join$drift_len_spec <- paste(drift_spec_size_join$drifts_unique,
                                      drift_spec_size_join$species,
                                      drift_spec_size_join$len, sep = "_")

drift_spec_size_join<- drift_spec_size_join %>%
  select(drift_len_spec)

## Ben 2020-11-11
## this has NA when there is no record from the original df
## we want all metadata to appear regardless of if there was a record there
## pivot wider starting with CP_MLML_to_2019 with columns to be species + length
## want drifts to be rows in piv-wider
## pivot longer which will have rows as drifts in one col and species + length. If not there will be NA
## left join metadata by drift
## qaqc df len should be 659*5252

cp_mlml_by_spec_len <- left_join(drift_spec_size_join, CP_MLML_to_2019,  by = "drift_len_spec")


eh <- drift_spec_size_join%>%
  rename(drift = drifts_unique)%>%
  select(drift, drift_spec_size)

eh_2 <- CP_MLML_to_2019 %>%
  unite(col = drift_spec_size, c(drift, species, length), sep = "_",
        remove = FALSE)

##DO NOT JOIN BY DRIFT
try_join <- left_join(eh, eh_2, by = "drift_spec_size")

```

