---
title: "blue cross corr from master II"
author: "Erin Johnston"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

```

```{r}

library(tidyverse)
library(here)


```

```{r}

full_cp_ml <- read_csv(here("Data/output", "2020-11-18_master_II.csv"))

blue_full <- full_cp_ml %>%
  filter(species == "BLU")

MOCI <- read_csv(here("Data", "Central_California_MOCI.csv"))

```

# Age Subset

```{r}

size_cutoff <- 21

juv <- blue_full %>%
  filter(size <= size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year,
           gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))
 
juv_2 <- juv %>%
  group_by(trip, area, site, month, day, year,
           gridcell) %>%
  summarise(cpue_cell = mean(cpue_sum))

juv_3 <- juv_2 %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell_2 = mean(cpue_cell))

juv_4 <- juv_3 %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell_2))

juv_atmp <- blue_full %>%
  filter(size <= size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year, gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))%>%
  group_by(trip, area, site, month, day, year,
           gridcell) %>%
  summarise(cpue_date = mean(cpue_sum)) %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_date)) %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))

juv_atmp2 <- blue_full %>%
  filter(size <= size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year, gridcell) %>%
  summarise(cpue_sum = sum(cpue))%>%
  group_by(trip, area, site, month, year, gridcell) %>%
  summarise(cpue_date = mean(cpue_sum)) %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_date)) %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))

juv_atmp3 <- blue_full %>%
  filter(size <= size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year, gridcell) %>%
  summarise(cpue_sum = sum(cpue))%>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_sum)) %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))

test <- anti_join(juv_atmp, juv_atmp3)

adult <- blue_full %>%
  filter(size > size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year,
           gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))

adult_2 <- blue_full %>%
  filter(size > size_cutoff)%>%
  group_by(drift, trip, area, site, month, day, year,
           gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))%>%
  group_by(trip, area, site, month, day, year,
           gridcell) %>%
  summarise(cpue_date = mean(cpue_sum)) %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_date)) %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))

full <- blue_full %>%
  group_by(drift, trip, area, site, month, day, year,
           gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))

full_2 <- blue_full %>%
  group_by(drift, trip, area, site, month, day, year,
           gridcell, anglerhours) %>%
  summarise(cpue_sum = sum(cpue))%>%
  group_by(trip, area, site, month, day, year,
           gridcell) %>%
  summarise(cpue_date = mean(cpue_sum)) %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_date)) %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))

juv_moci <- left_join(juv_4, MOCI, by = "year")

adult_moci <- left_join(adult_2, MOCI, by = "year")

full_moci <- left_join(full_2, MOCI, by = "year")

```


```{r loop set up}
headers_2 <- read_csv(here("Data", "headers_2.csv"))
juv_corr <- headers_2
adult_corr <- headers_2
full_corr <- headers_2

area_list <- list("PB", "BL", "AN", "PL")
site_list <- list("MPA", "REF")
season_list <- list("JFM", "AMJ", "JAS", "OND")
```

### Juvenile

```{r juvenile}
#for(i in species_list){
    for(j in area_list){
      for(k in site_list){
        for(l in season_list){
      juv_combos <- juv_moci%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(juv_combos$central_ca,
                        juv_combos$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr <- bind_rows(juv_corr, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
    }
#}

juv_combos <- juv_moci%>%
      filter(area == "PB", site == "MPA", season == "JFM")
cross_corr <- ccf(juv_combos$central_ca,
                        juv_combos$cpue_site, plot = F)


##

ggplot()+
  geom_point(data = juv_combos, aes(x = central_ca, y = cpue_site))

l = "JAS"

## ben 2020-12-10
## series plots MPA sites for each season + area

juv_corr <- juv_corr %>%
  arrange(desc(corr_values))
```

### Adult

```{r adult}
#for(i in species_list){
    for(j in area_list){
      for(k in site_list){
        for(l in season_list){
      adult_combos <- adult_moci%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(adult_combos$central_ca,
                        adult_combos$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_corr <- bind_rows(adult_corr, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
    }
#}

adult_corr <- adult_corr %>%
  arrange(desc(corr_values))

```

### Together

```{r all blue}

#for(i in species_list){
    for(j in area_list){
      for(k in site_list){
        for(l in season_list){
      full_combos <- full_moci%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(full_combos$central_ca,
                        full_combos$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_corr <- bind_rows(full_corr, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
    }
#}

full_corr <- full_corr %>%
  arrange(desc(corr_values))

```


# Without Protection Status

```{r}

headers_3 <- headers_2 %>%
  select(-site)
## _ns for no site
juv_corr_ns <- headers_3
adult_corr_ns <- headers_3
full_corr_ns <- headers_3

```

### Juvenile No Site

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      juv_combos_ns <- juv_moci%>%
      filter(area == j, season == l)
      cross_corr <- ccf(juv_combos_ns$central_ca,
                        juv_combos_ns$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr_ns <- bind_rows(juv_corr_ns, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

juv_corr_ns <- juv_corr_ns %>%
  arrange(desc(corr_values))

```

### Adult No Site

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      adult_combos_ns <- adult_moci%>%
      filter(area == j, season == l)
      cross_corr <- ccf(adult_combos_ns$central_ca,
                        adult_combos_ns$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_corr_ns <- bind_rows(adult_corr_ns, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

adult_corr_ns <- adult_corr_ns %>%
  arrange(desc(corr_values))

```

### Together No Site

```{r}
#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      full_combos_ns <- full_moci%>%
      filter(area == j, season == l)
      cross_corr <- ccf(full_combos_ns$central_ca,
                        full_combos_ns$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_corr_ns <- bind_rows(full_corr_ns, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

full_corr_ns <- full_corr_ns %>%
  arrange(desc(corr_values))

#full_corr_ns <- round(x = full_corr_ns$corr_values, digits = 4)


#lag0 <- juv_corr_ns %>%
#  filter(lag == 0)

vis <- full_corr_ns %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv <- juv_corr_ns %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_adult <- adult_corr_ns %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis$season <- factor(vis$season, levels = c("JFM", "AMJ", "JAS", "OND"))
vis_juv$season <- factor(vis_juv$season, levels = c("JFM", "AMJ", "JAS", "OND"))
vis_adult$season <- factor(vis_adult$season, levels = c("JFM", "AMJ", "JAS", "OND"))

```


```{r}



juv_moci_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -MOCI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.9), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())


adult_moci_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999",  "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_adult, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Adult Blue Rockfish Lag Correlation -MOCI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.8), breaks = seq(-0.6, 0.8, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8))+
  theme_bw()+
  facet_wrap(.~ area) +
  theme(panel.grid=element_blank())

full_moci_plot <-ggplot() +
  scale_color_manual(values = c( "#999999" ,  "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Blue Rockfish Lag Correlation -MOCI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.8), breaks = seq(-0.6, 0.8, 0.2),
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

ggplot() +
  scale_color_manual(values = c( "#999999" ,  "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis, aes(x = lag, y = corr_values,  color = season,
                                               fill = season))+
   labs(title = "Blue Rockfish Lag Correlation -MOCI", y = "correlation")+
   scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

#ggsave("2020-11-18_juv_moci_lag.png", plot = juv_moci_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_adult_moci_lag.png", plot = adult_moci_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_full_moci_lag.png", plot = full_moci_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)

## Grant 20202-11-18
## break down MOCI - component parts.
## include strongest lag in model
## use as exploration. Are there lags to consider. 
## explore, come up with Q's
## Is the a biological lag time in the response of cpue to moci?
## are the component parts of moci driving an overall pattern?
## are there differential spatial responses to oceanographic parameters
## is there a differential response between juveniles and adult rockfish?


```


```{r}

juv_moci_plot
adult_moci_plot
full_moci_plot

```


```{r, eval=F, include=F}

vis_juv_mpa <- juv_corr %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag)) %>%
  filter(site == "MPA")

vis_juv_ref <- juv_corr %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag)) %>%
  filter(site == "REF")

vis_juv_ref$season <- factor(vis_juv_ref$season, levels = c("JFM", "AMJ", "JAS", "OND"))


juv_moci_plot_mpa <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_ref, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -MOCI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  scale_y_continuous(limits = c(-0.2, 0.4), breaks = seq(-0.2, 0.4, 0.1))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

juv_moci_plot_mpa

```



# PDO

```{r}

pdo <- read_csv(here("Data", "pdo_noaa_ncei.csv")) %>%
  transform( year = substr(date, 1,4), month = substr(date, 5, 6))%>%
  filter(year %in% c(2007:2019))%>%
  mutate(season = case_when(
    month %in% c("01", "02", "03") ~ "JFM",
    month %in% c("04", "05", "06") ~ "AMJ",
    month %in% c("07", "08", "09") ~ "JAS",
    month %in% c("10", "11", "12") ~ "OND")) %>%
  group_by(year, season) %>%
  summarise(pdo_val = mean(value)) %>%
  mutate(year = as.numeric(as.character(year)))

  
juv_pdo <- left_join(juv_4, pdo, by = "year")

adult_pdo <- left_join(adult_2, pdo, by = "year")

full_pdo <- left_join(full_2, pdo, by = "year")

```


```{r}

juv_corr_pdo <- headers_3
adult_corr_pdo <- headers_3
full_corr_pdo <- headers_3

```

## Juv

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      juv_combos_pdo <- juv_pdo%>%
      filter(area == j, season == l)
      cross_corr <- ccf(juv_combos_pdo$pdo_val,
                        juv_combos_pdo$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr_pdo <- bind_rows(juv_corr_pdo, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

juv_corr_pdo <- juv_corr_pdo %>%
  arrange(desc(corr_values))



```

## Adult

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      adult_combos_pdo <- adult_pdo%>%
      filter(area == j, season == l)
      cross_corr <- ccf(adult_combos_pdo$pdo_val,
                        adult_combos_pdo$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_corr_pdo <- bind_rows(adult_corr_pdo, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

adult_corr_pdo <- adult_corr_pdo %>%
  arrange(desc(corr_values))


```

## Together

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      full_combos_pdo <- full_pdo%>%
      filter(area == j, season == l)
      cross_corr <- ccf(full_combos_pdo$pdo_val,
                        full_combos_pdo$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_corr_pdo <- bind_rows(full_corr_pdo, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

full_corr_pdo <- full_corr_pdo %>%
  arrange(desc(corr_values))

```


## Visualization

```{r}
vis_juv_pdo <- juv_corr_pdo %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv_pdo$season <- factor(vis_juv_pdo$season, levels = c("JFM", "AMJ", "JAS", "OND"))


vis_adult_pdo <- adult_corr_pdo %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_adult_pdo$season <- factor(vis_adult_pdo$season, levels = c("JFM", "AMJ", "JAS", "OND"))

vis_full_pdo <- full_corr_pdo %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_full_pdo$season <- factor(vis_full_pdo$season, levels = c("JFM", "AMJ", "JAS", "OND"))
```


```{r}

juv_pdo_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_pdo, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -PDO", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

adult_pdo_plot <-ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999",  "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_adult_pdo, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Adult Blue Rockfish Lag Correlation -PDO", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area) +
  theme(panel.grid=element_blank())

full_pdo_plot <- ggplot() +
  scale_color_manual(values = c( "#999999" ,  "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_full_pdo, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Blue Rockfish Lag Correlation -PDO", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
  theme(panel.grid=element_blank())

#ggsave("2020-11-18_juv_pdo_lag.png", plot = juv_pdo_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_adult_pdo_lag.png", plot = adult_pdo_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_full_pdo_lag.png", plot = full_pdo_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)

```

```{r}

juv_pdo_plot
adult_pdo_plot
full_pdo_plot

```



## PDO with protection status


```{r loop general setup}

headers <- data.frame(area = character(), site = character(), 
                      season = character(), lag = character(), corr_values = character())

juv_pdo_site <- headers
adult_pdo_site <- headers
full_pdo_site <- headers

area_list <- c("PB", "BL", "AN", "PL")
site_list <- c("MPA", "REF")
season_list <- c("JFM", "AMJ", "JAS", "OND")


```

```{r full loop}

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      full_combos_pdo_site <- full_pdo%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(full_combos_pdo_site$pdo_val,
                        full_combos_pdo_site$cpue_site, plot = F)
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_pdo_site <- bind_rows(full_pdo_site, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

    }
  }
}

```

I only need the negative lag values and seasons are plotted in alphabetical order unless I set them as factors with each name being a level.

```{r vis set up}

vis_full_pdo_site <- full_pdo_site %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_full_pdo_site$season <- factor(vis_full_pdo_site$season, levels = c("JFM", "AMJ", "JAS", "OND"))

full_pdo_site_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_full_pdo_site, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Blue Rockfish Lag Correlation -MPDO", y = "correlation",
       caption = "Fig 1")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.9), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.caption = element_text(size = 8))

```


```{r fig 1, fig.height= 6, fig.width= 10, fig.align= "center"}

full_pdo_site_plot

```


<div style="margin-bottom:50px;">
</div>

#### Juvenile vs Adult with protection status included

```{r juv vs adult loop}

## juv loop
for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juv_combos_pdo_site <- juv_pdo%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(juv_combos_pdo_site$pdo_val,
                        juv_combos_pdo_site$cpue_site, plot = T)
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_pdo_site <- bind_rows(juv_pdo_site, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

    }
  }
}

## adult loop
for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      adult_combos_pdo_site <- adult_pdo%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(adult_combos_pdo_site$pdo_val,
                        adult_combos_pdo_site$cpue_site, plot = F)
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_pdo_site <- bind_rows(adult_pdo_site, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

    }
  }
}

```


```{r juv vs adult set up}

## juv plot set up
vis_juv_pdo_site <- juv_pdo_site %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv_pdo_site$season <- factor(vis_juv_pdo_site$season, levels = c("JFM", "AMJ", "JAS", "OND"))

juv_pdo_site_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_pdo_site, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -PDO", y = "correlation",
       caption = "Fig 2")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.95), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.caption = element_text(size = 8))

## adult plot set up
vis_adult_pdo_site <- adult_pdo_site %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_adult_pdo_site$season <- factor(vis_adult_pdo_site$season, levels = c("JFM", "AMJ", "JAS", "OND"))

adult_pdo_site_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_adult_pdo_site, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Adult Blue Rockfish Lag Correlation -PDO", y = "correlation",
       caption = "Fig 3")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.9), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.caption = element_text(size = 8))

```


```{r fig 2, fig.height= 6, fig.width= 10, fig.align= "center"}

juv_pdo_site_plot

```

```{r fig 3, fig.height= 6, fig.width= 10, fig.align= "center"}

adult_pdo_site_plot

```

# MEI

```{r}

mei <- read_csv(here("Data", "mei_noaa.csv"))

mei_2 <- mei %>%
  pivot_longer(-year,
               names_to = "month",
               values_to = "value")%>%
  mutate(season = case_when(
    month %in% c("jan", "feb", "mar") ~ "JFM",
    month %in% c("apr", "may", "jun") ~ "AMJ",
    month %in% c("jul", "aug", "sep") ~ "JAS",
    month %in% c("oct", "nov", "dec") ~ "OND")) %>%
  group_by(year, season) %>%
  summarise(mei_val = mean(value)) %>%
  mutate(year = as.numeric(as.character(year)))

juv_mei <- left_join(juv_4, mei_2, by = "year")

adult_mei <- left_join(adult_2, mei_2, by = "year")

full_mei <- left_join(full_2, mei_2, by = "year")

```

```{r}

juv_corr_mei <- headers_3
adult_corr_mei <- headers_3
full_corr_mei <- headers_3

```


## Juv

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      juv_combos_mei <- juv_mei%>%
      filter(area == j, season == l)
      cross_corr <- ccf(juv_combos_mei$mei_val,
                        juv_combos_mei$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr_mei <- bind_rows(juv_corr_mei, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

juv_corr_mei <- juv_corr_mei %>%
  arrange(desc(corr_values))



```

## Adult

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      adult_combos_mei <- adult_mei%>%
      filter(area == j, season == l)
      cross_corr <- ccf(adult_combos_mei$mei_val,
                        adult_combos_mei$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_corr_mei <- bind_rows(adult_corr_mei, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

adult_corr_mei <- adult_corr_mei %>%
  arrange(desc(corr_values))


```

## Together

```{r}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      full_combos_mei <- full_mei%>%
      filter(area == j, season == l)
      cross_corr <- ccf(full_combos_mei$mei_val,
                        full_combos_mei$cpue_site, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_corr_mei <- bind_rows(full_corr_mei, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

full_corr_mei <- full_corr_mei %>%
  arrange(desc(corr_values))

```

## Visualization

```{r}
vis_juv_mei <- juv_corr_mei %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv_mei$season <- factor(vis_juv_mei$season, levels = c("JFM", "AMJ", "JAS", "OND"))


vis_adult_mei <- adult_corr_mei %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_adult_mei$season <- factor(vis_adult_mei$season, levels = c("JFM", "AMJ", "JAS", "OND"))

vis_full_mei <- full_corr_mei %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_full_mei$season <- factor(vis_full_mei$season, levels = c("JFM", "AMJ", "JAS", "OND"))
```


```{r}

juv_mei_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_mei, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -MEI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

adult_mei_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999",  "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_adult_mei, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Adult Blue Rockfish Lag Correlation -MEI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area) +
  theme(panel.grid=element_blank())

full_mei_plot <- ggplot() +
  scale_color_manual(values = c( "#999999" ,  "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_full_mei, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Blue Rockfish Lag Correlation -MEI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
  theme(panel.grid=element_blank())

#ggsave("2020-11-18_juv_mei_lag.png", plot = juv_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_adult_mei_lag.png", plot = adult_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_full_mei_lag.png", plot = full_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)

```

```{r}

juv_mei_plot
adult_mei_plot
full_mei_plot

```


# NOI?

https://coastwatch.pfeg.noaa.gov/erddap/griddap/erdlasNoix.htmlTable?noix%5B(2006-10-16T12:00:00Z):1:(2020-10-16T12:00:00Z)%5D

```{r, eval=F, include=F}

noi <- read_csv(here("Data", "noi_noaa.csv"))

noi <- noi %>%
  transform(year = substr(time, 1, 4), month = substr(time, 6, 7))%>%
  mutate(season = case_when(
    month %in% c("01", "02", "03") ~ "JFM",
    month %in% c("04", "05", "06") ~ "AMJ",
    month %in% c("07", "08", "09") ~ "JAS",
    month %in% c("10", "11", "12") ~ "OND")) %>%
  group_by(year, season) %>%
  summarise(noi_val = mean(noix)) %>%
  mutate(year = as.numeric(as.character(year)))

juv_noi <- left_join(juv, noi, by = "year")

adult_noi <- left_join(adult, noi, by = "year")

full_noi <- left_join(full, noi, by = "year")

```



```{r, eval=F, include=F}

juv_corr_noi <- headers_3
adult_corr_noi <- headers_3
full_corr_noi <- headers_3

```


## Juv

```{r, eval=F, include=F}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      juv_combos_noi <- juv_noi%>%
      filter(area == j, season == l)
      cross_corr <- ccf(juv_combos_noi$noi_val,
                        juv_combos_noi$cpue_sum, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr_noi <- bind_rows(juv_corr_noi, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

juv_corr_noi <- juv_corr_noi %>%
  arrange(desc(corr_values))



```

## Adult

```{r, eval=F, include=F}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      adult_combos_noi <- adult_noi%>%
      filter(area == j, season == l)
      cross_corr <- ccf(adult_combos_noi$noi_val,
                        adult_combos_noi$cpue_sum, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      adult_corr_noi <- bind_rows(adult_corr_noi, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

adult_corr_noi <- adult_corr_noi %>%
  arrange(desc(corr_values))


```

## Together

```{r, eval=F, include=F}

#for(i in species_list){
    for(j in area_list){
#      for(k in site_list){
        for(l in season_list){
      full_combos_noi <- full_noi%>%
      filter(area == j, season == l)
      cross_corr <- ccf(full_combos_noi$noi_val,
                        full_combos_noi$cpue_sum, plot = F) #plot = F
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      full_corr_noi <- bind_rows(full_corr_noi, c(area = j,  season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

        }
      }
#    }
#}

full_corr_noi <- full_corr_noi %>%
  arrange(desc(corr_values))

```

## Visualization

```{r, eval=F, include=F}
vis_juv_noi <- juv_corr_noi %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv_noi$season <- factor(vis_juv_noi$season, levels = c("JFM", "AMJ", "JAS", "OND"))


vis_adult_noi <- adult_corr_noi %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_adult_noi$season <- factor(vis_adult_noi$season, levels = c("JFM", "AMJ", "JAS", "OND"))

vis_full_noi <- full_corr_noi %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_full_noi$season <- factor(vis_full_noi$season, levels = c("JFM", "AMJ", "JAS", "OND"))
```



```{r, eval=F, include=F}

juv_noi_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_noi, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Correlation -NOI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
    theme(panel.grid=element_blank())

adult_noi_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999",  "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_adult_noi, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Adult Blue Rockfish Lag Correlation -NOI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area) +
  theme(panel.grid=element_blank())

full_noi_plot <- ggplot() +
  scale_color_manual(values = c( "#999999" ,  "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_full_noi, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Blue Rockfish Lag Correlation -NOI", y = "correlation")+
  scale_x_continuous(limits=c(-10.5,0.5),breaks=seq(-10,0,1))+
  theme_bw()+
  facet_wrap(.~ area)+
  theme(panel.grid=element_blank())

#ggsave("2020-11-18_juv_mei_lag.png", plot = juv_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_adult_mei_lag.png", plot = adult_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)
#ggsave("2020-11-18_full_mei_lag.png", plot = full_mei_plot, path = "C:/Users/erinj/Documents/Thesis/Figures/Lag", dpi = 1000, width = 8, height = 4)

```