---
title: "Correlation Loop Comparison"
author: "E.M. Johnston"
date: "3/2/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

```

```{r libraries and data}

library(tidyverse)
library(here)
library(patchwork)

juv_moci <- read_csv(here("Data", "2021-03-02_juv_moci_na.csv"))

```

`juv_moci` is the dataframe for juvenile Blue rockfish that has area, site, season, year, cpue values, and moci values.
```{r, echo=F}

juv_moci %>% head(3)

```


<div style="margin-bottom:80px;">
</div>

In this markdown you will find:

1) Correlation loop, visuals, and top correlation using ccf()
2) Correlation loop, visuals, and top correlation using hand calculation
3) Correlation loop, visuals, and top correlation using cor()
4) Side by side visuals from ccf() and cor()/hand calculation
5) ccf and acf code

## Correlations Calculated using CCF

```{r ccf loop set up}

juv_corr_ccf <- data.frame(area = character(), site = character(), season = character(), lag = character(), corr_values = character())  

area_list <- c("PB", "BL", "AN", "PL")
site_list <- c("MPA", "REF")
season_list <- c("JFM", "AMJ", "JAS", "OND")


```

```{r ccf loop and plot}

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juv_combos <- juv_moci%>%
      filter(area == j, site == k, season == l)
      cross_corr <- ccf(juv_combos$central_ca,
                        juv_combos$cpue_site, plot = F, na.action = na.pass)
      lag <- cross_corr$lag
      corr_values <- cross_corr$acf
      for(m in 1:length(lag)){
      juv_corr_ccf <- bind_rows(juv_corr_ccf, c(area = j, site = k, season = l, 
                                     lag = lag[m], corr_values = corr_values[m]))
      }

    }
  }
}

vis_juv_ccf <- juv_corr_ccf %>%
  filter(lag %in% c(-10:0))%>%
  mutate(corr_values = as.numeric(corr_values),
         lag = as.numeric(lag))

vis_juv_ccf$season <- factor(vis_juv_ccf$season, levels = c("JFM", "AMJ", "JAS", "OND"))

juv_ccf_plot <- ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = vis_juv_ccf, aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag Cross Correlation", y = "correlation",
       caption = "")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.95), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.title = element_text(hjust = 0.5),
          plot.caption = element_text(size = 8))



```

```{r fig 1, fig.height=6, fig.width=10, fig.align="center"}

juv_ccf_plot

```

#### top correlations from each area + site

```{r ccf slice}

vis_juv_ccf %>%
  arrange(desc(corr_values)) %>%
  group_by(area, site) %>%
  slice(1)

```

## Correlations Calculated using Equation

The equation being used is:

$r = \frac{\Sigma(x_{i}-\bar{x}) (y_{i} - \bar{y})}{\sqrt{\Sigma(x_{i}-\bar{x})^2\Sigma(y_{i}-\bar{y})^2}}$

```{r hand set up loop and plot}

juv_corr_hand <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())  


#i=0

#new_df <- 
  
for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_moci %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        cor <- (sum((lag_df$central_ca - mean(lag_df$central_ca, na.rm = T))* 
                      (lag_df$cpue_site - mean(lag_df$cpue_site, na.rm = T))))/
          ((sqrt(sum((lag_df$central_ca - mean(lag_df$central_ca, na.rm = T))^2)))*
             (sqrt(sum((lag_df$cpue_site - mean(lag_df$cpue_site, na.rm = T))^2))))
        for(m in 1:length(cor)){
          juv_corr_hand <- bind_rows(juv_corr_hand, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
}  
  

juv_vis_hand <- juv_corr_hand %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_hand$season <- factor(juv_vis_hand$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  



juv_hand_plot <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_hand, aes(x = lag, y = correlation, 
                                                         color = season, fill = season))+
  labs(title = "Juvenile Blue Rockfish Hand Calculation")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  theme_bw()+
  facet_grid(site~area)+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))
 


```

```{r fig 2, fig.height=6, fig.width=10, fig.align="center"}

juv_hand_plot

```

#### top correlations from each area + site

```{r hand slice}

juv_vis_hand %>%
  arrange(desc(correlation)) %>%
  group_by(area, site) %>%
  slice(1)

```

## Correlations Calculated using cor() function
### Just making sure it is the same as calculating by hand (**spoiler, it is the same**)

```{r cor set up loop and plot}

juv_corr_cor <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())  

  
for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile2 <- juv_moci %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df2 <- juvenile2 %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        cor2 <- cor(lag_df2$central_ca, lag_df2$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_cor <- bind_rows(juv_corr_cor, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor2[m]))
        }
      }
    }
  }
}  


juv_vis_cor <- juv_corr_cor %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_cor$season <- factor(juv_vis_cor$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

juv_cor_plot <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_cor, aes(x = lag, y = correlation, 
                                                        color = season, fill = season))+
  labs(title = "Juvenile Blue Rockfish cor()")+
  facet_grid(site ~ area)+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))
  



```

```{r fig 3, fig.height=6, fig.width=10, fig.align="center"}

juv_cor_plot

```


#### top correlations from each area + site

```{r cor slice}

juv_vis_cor %>%
  arrange(desc(correlation)) %>%
  group_by(area, site) %>%
  slice(1)

```

<div style="margin-bottom:80px;">
</div>


## Visual Comparison

This is just one example of the Ano Nuevo MPA, but the pattern is the same for all. There are some large lags popping out around 6, 7, and 8 years back. 

```{r comparison plot set up, echo=F}

ccf_plot <- vis_juv_ccf %>%
  filter(area == "AN", site == "MPA") %>%
  ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", aes(lag, y = corr_values,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag ccf()", y = "correlation",
       caption = "")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.95), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  #facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.title = element_text(hjust = 0.5),
          plot.caption = element_text(size = 8))

cor_plot <- juv_vis_cor %>%
  filter(area == "AN", site == "MPA") %>%
  ggplot() +
  scale_color_manual(values = c(  "#999999" , "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c( "#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", aes(lag, y = correlation,  color = season,
                                               fill = season))+
  labs(title = "Juvenile Blue Rockfish Lag cor()", y = "correlation",
       caption = "")+
  scale_x_continuous(limits=c(-8.5,0.5),breaks=seq(-8,0,1))+
  scale_y_continuous(limits = c(-0.6, 0.95), breaks = seq(-0.6, 0.9, 0.2), 
                     labels = c(-0.6, -0.4, -0.2, 0.0, 0.2, 0.4, 0.6, 0.8) )+
  theme_bw()+
  #facet_grid(site ~ area)+
    theme(panel.grid=element_blank(),
          plot.title = element_text(hjust = 0.5),
          plot.caption = element_text(size = 8))

```


```{r plot compare, fig.height=6, fig.width=10, fig.align="center"}

ccf_plot + cor_plot

```

<div style="margin-bottom:80px;">
</div>

## ccf() and acf() code

```{r ccf source code}

stats:::ccf

```

```{r acf source code}

stats:::acf

```




Meeting- CCF/Correlation? 2021-03-09 HG GW BR


