---
title: "CCFRP Data Formatting/Curation"
author: "Erin Johnston"
date: "3/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r libraries}

library(tidyverse)
library(here)

```

#### Metadata Information:

* **group** - either MLML(Moss Landing) or Cal Poly

* **trip** - two letter area code + 'T' + the trip number + two digit year
  * *example*: BLT01_20 is the first trip from Piedras Blancas in 2020.


* **area** - the broad area location sampled
  * AN: Ano Nuevo (MLML)
  * FN: Farallon Islands (MLML)
  * PL: Point Lobos (MLML)
  * BL: Piedras Blancas (Cal Poly)
  * PB: Point Buchon (Cal Poly)


* **site** - protection status
  * MPA: marine protected area
  * REF: associated reference site where fishing is allowed


* **month** - month sampled. July-September (rarely October)

* **day** - day sampled

* **year** - year sampled. 2007-2019

* **drift** - two letter area code + one letter site designation ('M' for MPA or 'R' for REF) + six digit date (MMDDYY) + two digit cell number + two digit drift number. 
  * *example*: BLR0722201202 would be the second drift from Piedras Blancas reference site on 7/22/2020 in cell 12.

* **gridcell** - two letter area code + two digit cell number. 
  * *example*: BL02 is cell #2 in Piedras Blancas

* **species** - see metadata file on species

* **length** - total length (tip of snout to end of tail) in centimeters

* **anglerhours** - total drift length (around 15 minutes) * number of anglers fishing (6-12 fishers) - any time that needs to be subtracted or added for anglers changing gear or taking breaks.

<div style="margin-bottom:40px;">
</div>

#### CCFRP Data Formatting

These data are for Cal Poly and Moss Landing from 2007-2019. 

```{r}

## 124,228 obs 12 vars
cp_ml <- read_csv(here("Data", "2021-03-12_CP_MLML_2007_2019.csv"))

cp_ml %>%
  select(everything())%>%
  summarise_all(funs(sum(is.na(.))))

```


There are 160 fishes with no length data - 75 fishes from Cal Poly, 85 from Moss Landing. There are 55 instances in which there are no angler hours. This came from one drift at Cal Poly. 

* CPUE - definitely drop the NA's for angler hours, but you can keep the 160 fishes without lengths. I looked at the paper data sheets for the 75 CP fishes and the only thing wrong with them is no recorded length, so they could potentially count for CPUE

* Biomass - drop all angler hour NA's and length NA's.

```{r}

## if you want to drop all NA for biomass or just to get rid of these, take out 'anglerhours'
## cp_ml <- cp_ml %>% drop_na()
cp_ml <- cp_ml %>%
  drop_na(anglerhours) 

## species count
spp_count <- cp_ml %>%count(species, sort = T)

## These are the 21 most abundant species
## 123,651 obs 13 vars
cp_ml <- cp_ml %>%
  filter(species %in% c("BLU", "GPR", "BLA", "OLV", "LCD", "VER", "DEA", "YTL",
                        "KLP", "CPR", "CNY", "CHN", "RSY", "BWN", "KGL", "QBK", 
                        "CBZ", "BAY", "PSD", "TRE", "SRY")) %>%
  unite("spec_size", species:length, sep = "_", remove = F)

```

See species metadata file for species information. `2021-03-12_CCFRP_metadata_species_table.csv`


```{r}
## code for adding zero

z_cp_ml <- cp_ml %>%
  count(spec_size, drift)%>%
  rename(num_caught = n) %>% 
  ## pivot_wider() creates wide dataframe 
  ## 659 rows are spec_size and the 5253 colums are drifts
  pivot_wider(names_from = drift,
              values_from = num_caught)%>% 
  ## pivot_longer() back to long format with NA
  pivot_longer(-spec_size,
               names_to = "drift",
               values_to = "num_caught") %>%
  ## turns NA's into 0 for number of fishes caught
  mutate(num_caught = case_when(
    is.na(num_caught) ~ 0,
    TRUE ~ as.numeric(num_caught)
  ))

## metadata
meta_cp_ml <- cp_ml %>%
  select(group, trip, area, site, month, day, year, gridcell, anglerhours, drift)%>%
  distinct()

## join zero infilled data and metadata

full_cp_ml <- left_join(z_cp_ml, meta_cp_ml, by = "drift") %>%
  ## calculate cpue
  mutate(cpue = num_caught/anglerhours)%>%
  separate(spec_size, into = c("species", "size"), sep = "_") %>%
  ## the code below is necessary to deal with some data inconsistencies 
  ## Moss Landing sometimes writes 'MPA/REF' instead of just one or the other
  ## this won't be necessary if you subset to just Cal Poly data
  rename(site_1 = site)%>%
  transform(site_2 = substr(drift, 3, 3))%>%
  mutate(
    site = case_when(
      site_2 == "M" ~ "MPA",
      site_2 == "R" ~ "REF"))%>%
  select(-site_1, - site_2)


#write_csv(full_cp_ml, here("Data/output", "2021-03-12_ccfrp_zeroinfill_species_subset.csv"))

```

<div style="margin-bottom:40px;">
</div>

#### CPUE at Different Levels

Example code for obtaining catch per unit effort at various levels of interest.

```{r}

### CPUE at the drift level
blue_drift <- full_cp_ml %>%
  filter(species == "BLU", area != "FN") %>%
  group_by(drift, trip, area, site, month, day, year, gridcell) %>%
  summarise(cpue_sum = sum(cpue))

### CPUE at the date level
blue_date <- blue_drift %>%
  group_by(trip, area, site, month, year, gridcell) %>%
  summarise(cpue_date = mean(cpue_sum))

### CPUE at the cell level
blue_cell <- blue_date  %>%
  group_by( area, site, year, gridcell) %>%
  summarise(cpue_cell = mean(cpue_date))

### CPUE at the site level
blue_site <- blue_cell %>%
  group_by( area, site, year) %>%
  summarise(cpue_site = mean(cpue_cell))



```

