---
title: '''Raw'' Data for Grant'
author: "Erin Johnston"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=F, message = F}

library(tidyverse)
library(here)

```

Reading in raw data for all years for four central coast regions.

```{r}
## actual raw data for CP and MLML 2007-2020, all species
cp_ml_20 <- read_csv(here("Data","2021-04-12_full_query_2007_2020.csv"))
```

NA values were dropped for species and for angler hours because those are necessary for CPUE calculations. Lengths that were missing were not excluded since this had no bearing on CPUE calculations and those fishes could still be counted without a length.

```{r}
## there is one drift (55 records) that are missing angler hours - dropping this
## there are three records missing a species identification - dropping this
## there are 165 fishes with no length. Will keep these in for the purposes of just CPUE
cp_ml_20 %>%
  select(everything())%>%
  summarise_all(funs(sum(is.na(.))))

cp_ml_20 <- cp_ml_20 %>% drop_na(c(anglerhours, species))
```

Uncommon species were filtered out of the data

```{r}
## 21 of the most common species
cp_ml_20_sp <- cp_ml_20 %>%
   filter(species %in% c("BLU", "GPR", "BLA", "OLV", "LCD", "VER", "DEA", "YTL",
                         "KLP", "CPR", "CNY", "CHN", "RSY", "BWN", "KGL", "QBK", 
                         "CBZ", "BAY", "PSD", "TRE", "SRY"))

counting_sp <- cp_ml_20_sp %>%
  count(species, drift)
```

Metadata for all lifetime drifts taken 2007-2020 were pulled from the database for inclusion, regardless of if any fishes were caught during those drifts to account for drifts in which no fish were caught.

```{r}
## there are 210 drifts for which no fish of any kind were caught
life_drifts <- read_csv(here("Data", "2021-04-12_lifetime_drifts_metadata.csv"))

## just the drifts, no metadata
## there are a total of 5639 drifts
drift <- life_drifts %>%
  select(drift)

## adding these 210 no data drifts to total
zero_wdrifts <- full_join(counting_sp, drift, by = "drift")

## checking to make sure there are total of 5639 unique drifts
length(unique(zero_wdrifts$drift))

zeros_long <- zero_wdrifts %>%
  rename(num_caught = n)%>%
  pivot_wider(names_from = drift,
              values_from = num_caught)%>%
  drop_na(species)%>%
  pivot_longer(-species,
                names_to = "drift",
                values_to = "num_caught")%>%
   mutate(num_caught = case_when(
     is.na(num_caught) ~ 0,
    TRUE ~ as.numeric(num_caught)
   ))


meta_cp_ml <- cp_ml_20_sp %>%
   select(group, trip, area, site, month, day, year, gridcell, anglerhours,drift)%>%
   distinct()

nofishdrifts <- anti_join(life_drifts, meta_cp_ml)


full_cp_ml <- left_join(zeros_long, life_drifts, by = "drift") %>%
   mutate(cpue = num_caught/anglerhour)


#write_csv(full_cp_ml, here("Data/output", "2021-05-04_airquotesraw_cpml_07_20.csv"))
```


Data Checks

```{r}
## checking to make sure that drifts with no fishes made it in to the final dataframe
checking <- full_cp_ml %>%
  filter(drift == "BLM0715083101")

## checking for NAs
full_cp_ml %>%
  select(everything())%>%
  summarise_all(funs(sum(is.na(.))))

## one of the drifts that didn't have any fishes also is missing angler hours.
full_cp_ml %>% filter_all(any_vars(is.na(.))) 

## making sure there are still 5639 unique drifts which match # lifetime drifts
length(unique(full_cp_ml$drift))

```

