---
title: "Excluding Years from Analysis"
author: "Erin Johnston"
date: "6/23/2021"
output: 
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

[back](https://erinmarjo.github.io/CCFRP/27_thesis_progress_report.html)

```{r libraries, message=F, warning = F}

library(tidyverse)
library(here)

```


## Missing Heatwave Years

Taking out all CPUE & MOCI data from 2014, 2015, 2016. Doing this shoud wipe out the 2 year lag correlation if the juvenile abundance is in response to things happening during MHW. Basically, if the MHW is driving this relationship, we shoul see less of a relationship.

```{r, echo = F}

juv_blue <- read_csv(here("Data", "2021-07-04_juv_blue_moci_site_cpue.csv"))

juv_no_mhw <- juv_blue %>%
  rename(central_ca2 = central_ca,
         cpue_site2 = cpue_site) %>%
  mutate(cpue_site = case_when(
    year %in% c(2013, 2014, 2015) ~ NA_real_, ## NA_real_ instead of NA so that R doesn't complain about input needing to be a logical vector instead of a double vector
    year %in% c(2007:2012, 2016:2020) ~ as.numeric(cpue_site2)
    ), central_ca = case_when(
      year %in% c(2013, 2014, 2015) ~ NA_real_,
      year %in% c(2007:2012, 2016:2020) ~ as.numeric(central_ca2)
    ))

#juv_no_mhw <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_mhw.csv"))

juv_corr_no_mhw <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())


area_list <- c("PB", "BL", "AN", "PL")
site_list <- c("MPA", "REF")
season_list <- c("JFM", "AMJ", "JAS", "OND")

erin_ccf <- function(full_x, full_y, lag_x_rm, lag_y_rm) {
  mean_x <- mean(full_x, na.rm = T)
  mean_y <- mean(full_y, na.rm = T)
  corval <- (sum((lag_x_rm - mean_x)*
                   (lag_y_rm - mean_y)))/
    ((sqrt(sum((full_x - mean_x)^2, na.rm = T)))*
       (sqrt(sum((full_y - mean_y)^2, na.rm = T))))
  return(corval)
  
}

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_mhw %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_mhw <- bind_rows(juv_corr_no_mhw, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_mhw <- juv_corr_no_mhw %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_mhw$season <- factor(juv_vis_no_mhw$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

juv_plot_no_mhw <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_mhw, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No MHW Year Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)
```


```{r, echo = F}

juv_plot_no_mhw

```

## Missing Three Random Years

Taking out all CPUE & MOCI data from 2009-2011. Taking out a random subset of three consecutive years that are *not* marine heatwave years, should mean that the correlation is not completely gone. I would expect to still see a two-ish year lag for many of the area+ site combinations for juv blue rockfish if the MHW are driving the relationship, since those years are still included.

```{r , echo = F}

juv_no_9_11 <- juv_blue %>%
  rename(central_ca2 = central_ca,
         cpue_site2 = cpue_site) %>%
  mutate(cpue_site = case_when(
    year %in% c(2009, 2010, 2011) ~ NA_real_, 
    year %in% c(2007, 2008, 2012:2020) ~ as.numeric(cpue_site2)
    ), central_ca = case_when(
      year %in% c(2009, 2010, 2011) ~ NA_real_,
      year %in% c(2007, 2008, 2012:2020) ~ as.numeric(central_ca2)
    ))


#juv_no_9_11 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_09-11.csv"))

juv_corr_no_9_11 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_9_11 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_9_11 <- bind_rows(juv_corr_no_9_11, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_9_11 <- juv_corr_no_9_11 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_9_11$season <- factor(juv_vis_no_9_11$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no9_11<- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_9_11, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2009-2011 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

juv_vis_no_9_11 %>%
  arrange(desc(correlation)) %>%
  group_by(area, site) %>%
  slice(1)

```

## Excluding 2007-2009

```{r, echo = F}

juv_no_7_9 <- juv_blue %>%
  rename(central_ca2 = central_ca,
         cpue_site2 = cpue_site) %>%
  mutate(cpue_site = case_when(
    year %in% c(2007:2009) ~ NA_real_, 
    year %in% c(2010:2020) ~ as.numeric(cpue_site2)
    ), central_ca = case_when(
      year %in% c(2007:2009) ~ NA_real_,
      year %in% c(2010:2020) ~ as.numeric(central_ca2)
    ))

#juv_no_7_9 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_07-09.csv"))

juv_corr_no_7_9 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_7_9 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_7_9 <- bind_rows(juv_corr_no_7_9, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_7_9 <- juv_corr_no_7_9 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_7_9$season <- factor(juv_vis_no_7_9$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no7_9 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_7_9, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2007-2009 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

no7_9

```

## Excluding 2008-2010

```{r, echo = F}

juv_no_8_10 <- juv_blue %>%
  rename(central_ca2 = central_ca,
         cpue_site2 = cpue_site) %>%
  mutate(cpue_site = case_when(
    year %in% c(2008:2010) ~ NA_real_, 
    year %in% c(2007, 2011:2020) ~ as.numeric(cpue_site2)
    ), central_ca = case_when(
      year %in% c(2008:2010) ~ NA_real_,
      year %in% c(2007, 2011:2020) ~ as.numeric(central_ca2)
    ))

# juv_no_8_10 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_08-10.csv"))

juv_corr_no_8_10 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_8_10 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_8_10 <- bind_rows(juv_corr_no_8_10, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_8_10 <- juv_corr_no_8_10 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_8_10$season <- factor(juv_vis_no_8_10$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no8_10 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_8_10, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2008-2010 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

no8_10

```

## Excluding 2009-2011

```{r, echo = F}
no9_11

```


## Excluding 2010-2012

```{r, echo = F}

juv_no_10_12 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_10-12.csv"))

juv_corr_no_10_12 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_10_12 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_10_12 <- bind_rows(juv_corr_no_10_12, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_10_12 <- juv_corr_no_10_12 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_10_12$season <- factor(juv_vis_no_10_12$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no10_12 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_10_12, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2010-2012 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

no10_12

```

## Excluding 2011-2013

```{r, echo = F}

juv_no_11_13 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_11-13.csv"))

juv_corr_no_11_13 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_11_13 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_11_13 <- bind_rows(juv_corr_no_11_13, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_11_13 <- juv_corr_no_11_13 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_11_13$season <- factor(juv_vis_no_11_13$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no11_13 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_11_13, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2011-2013 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

no11_13

```


## Excluding 2017-2019

```{r, echo = F}

juv_no_17_19 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_17-19.csv"))

juv_corr_no_17_19 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_17_19 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_17_19 <- bind_rows(juv_corr_no_17_19, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_17_19 <- juv_corr_no_17_19 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_17_19$season <- factor(juv_vis_no_17_19$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no17_19 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_17_19, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2017-2019 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)

no17_19

```


## Excluding 2018-2020 

```{r, echo = F}

juv_no_18_20 <- read_csv(here("Data", "2021-04-13_juv_moci_na_no_18-20.csv"))

juv_corr_no_18_20 <- data.frame(area = character(), site = character(), season = character(), lag = character(), correlation = character())

for(j in area_list){
  for(k in site_list){
    for(l in season_list){
      juvenile <- juv_no_18_20 %>%
        filter(area == j, site == k, season == l)
      for(i in 0:8){
        lag_df <- juvenile %>%
          mutate(central_ca = dplyr::lag(central_ca, n = i)) %>% drop_na()
        #juvenile2 <- juvenile %>% drop_na()
        cor <- erin_ccf(juvenile$central_ca, juvenile$cpue_site,
                        lag_df$central_ca, lag_df$cpue_site)
        for(m in 1:length(cor)){
          juv_corr_no_18_20 <- bind_rows(juv_corr_no_18_20, c(area = j, site = k, season = l, 
                                            lag = -i, correlation = cor[m]))
        }
      }
    }
  }
} 

juv_vis_no_18_20 <- juv_corr_no_18_20 %>%
  mutate(correlation = as.numeric(correlation),
         lag = as.numeric(lag))
  
juv_vis_no_18_20$season <- factor(juv_vis_no_18_20$season, levels = c("JFM", "AMJ" ,"JAS", "OND"))  

no18_20 <- ggplot()+
  scale_color_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  scale_fill_manual(values = c("#999999", "#009999", "#666666", "#000000"))+
  geom_col(position = "dodge2", data = juv_vis_no_18_20, aes(x = lag, y = correlation, color = season, fill = season))+
  labs(title = "No 2018-2020 Data")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5))+
  facet_grid(site~area)


no18_20

```


[back](https://erinmarjo.github.io/CCFRP/27_thesis_progress_report.html)


```{r, eval = F, echo=F}

# Run this in console: rmarkdown::render(input = here("Code", "28_DATA_year_exclusion.Rmd"), output_dir = here("docs"))

```
