---
title: "Master Dataset 2007-2020"
author: "Erin Johnston"
date: "7/3/2021"
output: 
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r libraries, warning=F, message=F}

library(tidyverse)
library(here)

```

This documents the steps taken to create the master dataframe for CCFRP data from 2007-2020 with CPUE and size for the 21 most common species represented.

Data were queried from the new statewide CCFRP database for information regarding fishes caught by Cal Poly and Moss Landing Marine Laboratories (MLML) during CCFRP tripsfrom 2007 to 2020. 

Information includes: group, trip, drift, area, site, month, day, year, gridcell, species, length, and angler hours.

## Initial Data

* Raw data were read in and NA's were investigated and dropped if fitting. 
* Species were filtered to include only the most common species caught between the two institutuions. 
* A new column was create which combined the species and size of each record (fish).


```{r initial data}

cp_ml_20 <- read_csv(here("Data","2021-04-12_full_query_2007_2020.csv"))

cp_ml_20 %>%
  select(everything())%>%
  summarise_all(funs(sum(is.na(.))))

cp_ml_20 <- cp_ml_20 %>% drop_na()

cp_ml_20_sp <- cp_ml_20 %>%
   filter(species %in% c("BLU", "GPR", "BLA", "OLV", "LCD", "VER", "DEA", "YTL",
                         "KLP", "CPR", "CNY", "CHN", "RSY", "BWN", "KGL", "QBK", 
                         "CBZ", "BAY", "PSD", "TRE", "SRY"))%>%
  unite(col = spec_size, species:length, sep = "_")

```

## Data Restructuring

* Records were counted for each unique species-size combination that occurred on each drift
* To account for drifts in which a certain species-size was not caught, 0's were added.
* This dataframe was combined with the corresponding metadata

```{r data restructuring}

z_cp_ml <- cp_ml_20_sp %>%
   count(spec_size, drift)%>%
   rename(num_caught = n) %>% 
   pivot_wider(names_from = drift,
               values_from = num_caught)%>% 
   pivot_longer(-spec_size,
                names_to = "drift",
                values_to = "num_caught") %>%
   mutate(num_caught = case_when(
     is.na(num_caught) ~ 0,
    TRUE ~ as.numeric(num_caught)
   ))

meta_cp_ml <- cp_ml_20_sp %>%
   select(group, trip, area, site, month, day, year, gridcell, anglerhours, drift)%>%
   distinct()

full_cp_ml <- left_join(z_cp_ml, meta_cp_ml, by = "drift") %>%
   mutate(cpue = num_caught/anglerhours)%>%
   separate(spec_size, into = c("species", "size"), sep = "_") %>%
   rename(site_1 = site)%>%
   transform(site_2 = substr(drift, 3, 3))%>%
   mutate(
     site = case_when(
       site_2 == "M" ~ "MPA",
       site_2 == "R" ~ "REF"))%>%
   select(-site_1, - site_2)%>%
   mutate(size = as.numeric(size))

```

## Adding Missing Drifts

* To account for drifts where there was no catch, the statewide database was queried for each unique drift from 2007 to 2020. 
* When compared with the number of drifts in the full dataset, there were 210 drifts missing
* These drifts were added for each of the 21 species in a new dataframe


```{r}

data_drifts <- full_cp_ml %>%
  select(drift) %>%
  distinct()

life_drifts <- read_csv(here("Data", "2021-04-12_lifetime_drifts_metadata.csv"))


missing_drift <- anti_join(life_drifts, data_drifts, by = "drift")


rf_list <- c("BLU", "GPR", "BLA", "OLV", "LCD", "VER", "DEA", "YTL", "KLP",
             "CPR", "CNY", "CHN", "RSY", "BWN", "KGL", "QBK", "CBZ", "BAY", 
             "PSD", "TRE", "SRY")

add_drift_df <- data.frame(group = character(), trip = character(), drift = character(),
                           area = character(), site = character(), month = character(), 
                           day = character(), year = double(), gridcell = character(),
                           anglerhours = double())

for(i in rf_list){
  add_drifts <- missing_drift %>%
    mutate(species = i,
            num_caught = 0,
            cpue = num_caught/anglerhour) %>%
    rename(anglerhours = anglerhour,
           site_1 = site)%>%
    transform(site_2 = substr(drift, 3, 3))%>%
    mutate(site = case_when(
       site_2 == "M" ~ "MPA",
       site_2 == "R" ~ "REF"))%>%
    select(-site_1, - site_2)
  add_drift_df <- bind_rows(add_drift_df, add_drifts)
}

```

## The Full Master Dataset

The 210 missing drifts for each of the 21 species were added to the full dataset to create a master dataset that was used for analysis

```{r}

full_master <- full_cp_ml %>%
  bind_rows(add_drift_df)

```

