---
title: "Figure Dump Code"
author: "Erin Johnston"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = F,
                      message = F)
```

```{r libraries}

library(tidyverse)
library(here)
library(patchwork)
library(plotrix)
library(ggridges)

```

```{r data}

master <- read_csv(here("Data", "2021-06-28_full_master_2020.csv"))

moci <- read_csv(here("Data", "CaliforniaMOCI_JFM1991-AMJ2021.csv"))

```


Wish list of figure dump:

* CPUE line graph blue rockfish – each area and site… with error bars
* BPUE line graph blue rockfish
* CPUE vs size dot plot... broken up by area + site and also together
* MOCI line graph
* MOCI bar chart colored blue and red
* Length frequency bar charts
* Length frequency density plots
* Mean length box and whisker plots
* MOCI/CPUE lag figures – adults, juvenile, together
* Top MOCI/CPUE correlation
* No MHW vs no data from other three years in a row

## CPUE line graph

Might want to think of more interesting ways to visualize CPUE than just line graphs with error bars. Ditto BPUE.

```{r cpue figures}

# check <- blue_bpue %>%
#   filter(is.na(class))

## these are drift added in where there were no blues caught
## need to assign these as both Juvenile and Adult in order to break up by 'class'
class_j <- master %>%
  filter(species == "BLU", is.na(size), !is.na(cpue)) %>%
  mutate(class = "Juvenile")

class_a <- master %>%
  filter(species == "BLU", is.na(size), !is.na(cpue)) %>%
  mutate(class = "Adult")

## original missing years df
missing_bl_blue <- data.frame(area = c("BL", "BL", "BL", "BL"),
                              site = c("REF", "MPA", "REF", "MPA"),
                              year = c(2007, 2007, 2015, 2015), 
                              cpue_site = c(NA, NA, NA, NA))

## creating dataframe with missing years to bind to CPUE data frame
## without these missing points, 2015 BL is an average of the years around it
## can not bind these if people would like to see this as an average
missing_bl_blue2 <- data.frame(area = c("BL", "BL", "BL", "BL", "BL", "BL", "BL", "BL"),
                              site = c("REF", "REF", "MPA", "MPA", "REF", "REF", "MPA", "MPA"),
                              year = c(2007, 2007, 2007, 2007, 2015, 2015, 2015, 2015), 
                              class = c("Juvenile", "Adult", "Juvenile", "Adult", 
                                        "Juvenile", "Adult", "Juvenile", "Adult"),
                              cpue_site = c(NA, NA, NA, NA, NA, NA, NA, NA),
                              se_site = c(NA, NA, NA, NA, NA, NA, NA, NA))

## df for cpue vis
blue_cpue <- master %>%
  filter(species == "BLU", !is.na(cpue)) %>%
  mutate(class = case_when(
    size <= 21 ~ "Juvenile", 
    size > 21 ~ "Adult"
  )) %>%
  filter(!is.na(size)) %>%
  bind_rows(class_j, class_a) %>%
  group_by(drift, trip, area, site, month, day, year, gridcell, class) %>%
  summarise(cpue_drift = sum(cpue))%>%
  group_by(trip, area, site, month, day, year, gridcell, class) %>%
  summarise(cpue_date = mean(cpue_drift)) %>%
  group_by( area, site, year, gridcell, class) %>%
  summarise(cpue_cell = mean(cpue_date)) %>%
  group_by( area, site, year, class) %>%
  summarise(cpue_site = mean(cpue_cell),
            se_site = std.error(cpue_cell))%>%
  bind_rows(missing_bl_blue2) %>%
  mutate(area = case_when(
    area == "AN" ~ "A\U00F1o Nuevo",
    area == "PL" ~ "Point Lobos",
    area == "BL" ~ "Piedras Blancas",
    area == "PB" ~ "Point Buchon"
  ))

## ordering from N to S
blue_cpue$area <- factor(blue_cpue$area, levels = c("A\U00F1o Nuevo", "Point Lobos", 
                                                    "Piedras Blancas", "Point Buchon"))

## CPUE together
adult_juv_cpue <- ggplot(data = blue_cpue, aes(x = year, y = cpue_site, 
                                               color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = cpue_site - se_site, ymax = cpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 2))+
  labs(y = "CPUE (number of fishes/angler hours\n", x = "")+
  facet_grid(area ~ class) +
  theme_bw()+
  theme(panel.grid = element_blank())


## juvenile CPUE
juv_cpue <- blue_cpue %>%
  filter(class == "Juvenile") %>%
  ggplot(aes(x = year, y = cpue_site, color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = cpue_site - se_site, ymax = cpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 1))+
  labs(y = "CPUE (number of fishes/angler hours\n", x = "",
       caption = "Juvenile")+
  facet_grid(area ~ .) +
  theme_bw()+
  theme(panel.grid = element_blank())

## adult CPUE
adult_cpue <- blue_cpue %>%
  filter(class == "Adult") %>%
  ggplot(aes(x = year, y = cpue_site, color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = cpue_site - se_site, ymax = cpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 1))+
  labs(y = "CPUE (number of fishes/angler hours\n", x = "",
       caption = "Adult")+
  facet_grid(area ~ .) +
  theme_bw()+
  theme(panel.grid = element_blank())

## We can have visuals for each area... or class by using filter()
## for example, Point Buchon with juveniles and adults would look like this

pb <- blue_cpue %>%
  filter(area == "Point Buchon") %>%
  ggplot(aes(x = year, y = cpue_site, color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = cpue_site - se_site, ymax = cpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 1))+
  labs(y = "CPUE (number of fishes/angler hours\n", x = "",
       caption = "Point Buchon")+
  facet_grid(class~ .) +
  theme_bw()+
  theme(panel.grid = element_blank())

## save plots with this code
# ggsave("pb_cpue.png", plot = pb, dpi = 1000, width = 8, height = 7, path = here("Images/figure_dump"))



```

## BPUE line graph

```{r bpue figures}

bpue_0 <- master %>%
  filter(species == "BLU", num_caught == 0) %>%
  select(-num_caught) %>%
  mutate(biomass = 0)

## same as missing df above, but with bpue_site instead of cpue_site
missing_bl_blue3 <- data.frame(area = c("BL", "BL", "BL", "BL", "BL", "BL", "BL", "BL"),
                              site = c("REF", "REF", "MPA", "MPA", "REF", "REF", "MPA", "MPA"),
                              year = c(2007, 2007, 2007, 2007, 2015, 2015, 2015, 2015), 
                              class = c("Juvenile", "Adult", "Juvenile", "Adult", 
                                        "Juvenile", "Adult", "Juvenile", "Adult"),
                              bpue_site = c(NA, NA, NA, NA, NA, NA, NA, NA),
                              se_site = c(NA, NA, NA, NA, NA, NA, NA, NA))

## this is the step that is really different between CPUE figures and BPUE figures
## cleaned this so that after uncounting, I added back in all the drifts where the BPUE would have been 0 so that BPUE is not artifically inflated when averaging across levels
blue_bpue <- master %>%
  filter(species == "BLU", !is.na(size)) %>%
  mutate(biomass = 0.0158*size^2.988) %>%
  uncount(num_caught) %>%
  bind_rows(bpue_0) %>%
  mutate(class = case_when(
    size <= 21 ~ "Juvenile", 
    size > 21 ~ "Adult"
  )) %>%
  filter(!is.na(size)) %>%
  mutate(bpue = biomass/anglerhours) %>%
  group_by(drift, trip, area, site, month, day, year, gridcell, class) %>%
  summarise(bpue_drift = sum(bpue))%>%
  group_by(trip, area, site, month, day, year, gridcell, class) %>%
  summarise(bpue_date = mean(bpue_drift)) %>%
  group_by( area, site, year, gridcell, class) %>%
  summarise(bpue_cell = mean(bpue_date)) %>%
  group_by( area, site, year, class) %>%
  summarise(bpue_site = mean(bpue_cell),
            se_site = std.error(bpue_cell))%>%
  bind_rows(missing_bl_blue3) %>%
  mutate(area = case_when(
    area == "AN" ~ "A\U00F1o Nuevo",
    area == "PL" ~ "Point Lobos",
    area == "BL" ~ "Piedras Blancas",
    area == "PB" ~ "Point Buchon"
  ))

## ordering from N to S
blue_bpue$area <- factor(blue_bpue$area, levels = c("A\U00F1o Nuevo", "Point Lobos", 
                                                    "Piedras Blancas", "Point Buchon"))

## BPUE together
adult_juv_bpue <- ggplot(data = blue_bpue, aes(x = year, y = bpue_site, 
                                               color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = bpue_site - se_site, ymax = bpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 2))+
  labs(y = "BPUE (biomass/angler hours\n", x = "")+
  facet_grid(area ~ class) +
  theme_bw()+
  theme(panel.grid = element_blank())

## juvenile BPUE
juv_bpue <- blue_bpue %>%
  filter(class == "Juvenile") %>%
  ggplot(aes(x = year, y = bpue_site, color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = bpue_site - se_site, ymax = bpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 1))+
  labs(y = "BPUE (biomass/angler hours\n", x = "",
       caption = "Juvenile")+
  facet_grid(area ~ .) +
  theme_bw()+
  theme(panel.grid = element_blank())

## adult BPUE
adult_bpue <- blue_bpue %>%
  filter(class == "Adult") %>%
  ggplot(aes(x = year, y = bpue_site, color = site, group = site))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = bpue_site - se_site, ymax = bpue_site + se_site), width = 0.2)+
  scale_color_manual(values = c("#CC0000", "#0066CC"))+
  scale_x_continuous(limits = c(2007, 2020), breaks = seq(2007, 2020, 1))+
  labs(y = "BPUE (biomass/angler hours\n", x = "",
       caption = "Adult")+
  facet_grid(area ~ .) +
  theme_bw()+
  theme(panel.grid = element_blank())

#ggsave("adult_bpue.png", plot = adult_bpue, dpi = 1000, width = 8, height = 7, path = here("Images/figure_dump"))

```


```{r, echo = F, eval = F}

## this takes a long time to run. Do only if necessary to fix code

# t <- master %>%
#   filter(species == "BLU")%>%
#   ggplot()+
#   geom_point(aes(x = size, y = cpue), shape = 21, color = "black", fill = "white", size = 1)+
#   facet_grid(site ~ area)+
#   theme_bw()+
#   theme(panel.grid = element_blank())
# 
# ggsave("cpue_by_size_as.png", plot = t, dpi = 1000, width = 8, height = 7, path = here("Images/figure_dump"))

```


## MOCI Graphs

```{r moci}

moci_central <- moci %>%
  select(year, season, central_ca) %>%
  filter(year %in% c(1991:2020)) %>%
  group_by(year) %>%
  summarize(av_central = mean(central_ca))

moci_1SD_pos <- moci_central %>%
  filter(av_central > 3.97499)
moci_1SD_neg <- moci_central %>%
  filter(av_central < -3.97499)

sd(moci$central_ca) ## 3.97499
mean(moci$central_ca) ## -4.834653e-17 pretty close to 0


moci_jas <- moci %>%
  select(year, season, north_ca, central_ca) %>%
  filter(year %in% c(1991:2020), season == "JAS")

sd(moci_jas$central_ca) ## 3.97499
mean(moci_jas$central_ca)

jas_1SD_pos <- moci_jas %>%
  filter(central_ca > 3.560993, north_ca > 3.770262)

jas_1SD_neg <- moci_jas %>%
  filter(central_ca <= -3.560993, north_ca <= 3.770262)



ggplot()+
  ## in red, the MOCI value for JAS
  geom_point(data = moci_jas, aes(year, central_ca), color = "red")+
  geom_line(data = moci_jas, aes(year, central_ca), color = "red")+
  ## in blue, the MOCI value for all seasons
  geom_point(data = moci_central, aes(year, av_central), color = "blue")+
  geom_line(data = moci_central, aes(year, av_central), color = "blue")+
  ## solid line at the mean MOCI value
  geom_hline(yintercept = 0)+
  ## dashed line at one standard deviation
  geom_hline(yintercept = 3.993048, linetype = "dashed")+
  geom_hline(yintercept = -3.993048, linetype = "dashed")+
  labs(x = "", y = "MOCI", title = "Central Coast MOCI JAS vs All Seasons",
       caption = "Data Source: http://www.faralloninstitute.org/moci")+
  ## continuous years
  scale_x_continuous(limits=c(1990,2020),breaks=seq(1990,2020,2))+
  theme_bw()+
        ## puts box around graph
  theme(panel.grid=element_blank(),
        ## centers the title, controls size
        plot.title = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size=10),
        plot.caption = element_text(size = 5))+
  ## my attempt at a legend
  annotate(geom = "text", x = 1995, y = 10, label = "All",colour = "blue") + 
  annotate(geom = "text", x = 1995, y = 9, label = "JAS", 
           color = "red")+
  annotate(geom = "text", x = 1995, y = 8, label = "--- 1 SD", color = "black")


ggplot()+
  geom_point(data = moci_jas, aes(year, central_ca), shape = 21, colour = "black", 
                                  fill = "white", size = 2)+
  geom_line(data = moci_jas, aes(year, central_ca))+
  geom_point(data = jas_1SD_pos, aes(year, central_ca), color = "red", size = 2)+
  geom_point(data = jas_1SD_neg, aes(year, central_ca), color = "blue", size = 2)+
  geom_hline(yintercept = 0)+
  geom_hline(yintercept = 3.560993, linetype = "dashed")+
  geom_hline(yintercept = -3.560993, linetype = "dashed")+
  labs(x = "", y = "MOCI", title = "Central Coast Summer MOCI 1991-2020",
       caption = "Data Source: http://www.faralloninstitute.org/moci")+
  scale_x_continuous(limits=c(1991,2020),breaks=seq(1991,2020,2))+
  theme_bw()+
  theme(panel.grid=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size=10),
        plot.caption = element_text(size = 5))

moci_yr_avg <- ggplot()+
  geom_point(data = moci_central, aes(year, av_central), shape = 21, colour = "black", 
                                  fill = "white", size = 2)+
  geom_line(data = moci_central, aes(year, av_central))+
  geom_point(data = moci_1SD_pos, aes(year, av_central), color = "red", size = 2)+
  geom_point(data = moci_1SD_neg, aes(year, av_central), color = "blue", size = 2)+
  geom_hline(yintercept = 0)+
  geom_hline(yintercept = 3.97499, linetype = "dashed")+
  geom_hline(yintercept = -3.97499, linetype = "dashed")+
  labs(x = "", y = "MOCI", title = "Central Coast MOCI 1991-2020",
       caption = "Data Source: http://www.faralloninstitute.org/moci")+
  scale_x_continuous(limits=c(1991,2020),breaks=seq(1991,2020,2))+
  theme_bw()+
  theme(panel.grid=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size=10),
        plot.caption = element_text(size = 5))


moci_central2 <- moci %>%
  select(year, season, central_ca) %>%
  filter(year %in% c(1991:2020)) %>%
  mutate(pos_neg = case_when(
    central_ca > 0 ~ "positive",
    central_ca < 0 ~ "negative"
  ))


ggplot() +
  geom_col(data = moci_central2, position = position_dodge2(), 
           aes(x = year, y = central_ca, color = pos_neg, fill = pos_neg))+
  geom_line(data = moci_central, aes(x = year, y = av_central), size = 1)+
  scale_fill_manual(values = c( "#0066CC", "#CC0000"))+
  scale_color_manual(values = c( "#00008B", "#8B0000")) +
  scale_x_continuous(limits=c(1990,2021),breaks=seq(1990,2021,2))+
  labs(y = "MOCI",  x = "")+
  theme_bw()+
  theme(panel.grid = element_blank())


## spline of the averages looks a little better for vis.
## make spline this way
spline.moci<- as.data.frame(spline(moci_central2$year, moci_central2$central_ca))


moci_bar <- ggplot() +
  geom_col(data = moci_central2, position = position_dodge2(), 
           aes(x = year, y = central_ca, color = pos_neg, fill = pos_neg))+
  geom_line(data = spline.moci, aes(x = x, y = y), size = 1)+
  geom_hline(yintercept = 0)+
  scale_fill_manual(values = c( "#0066CC", "#CC0000"))+
  scale_color_manual(values = c( "#00008B", "#8B0000")) +
  scale_x_continuous(limits=c(1990,2021),breaks = seq(1990, 2021, 2))+
  scale_y_continuous(limits = c(-8, 11), breaks = seq(-8, 11, 2))+
  labs(y = "MOCI",  x = "", caption = "Data Source: http://www.faralloninstitute.org/moci")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        legend.position = "none",
        plot.caption = element_text(size = 5))


#ggsave("moci_yr_avg.png", plot = moci_yr_avg, dpi = 1000, width = 8, height = 6, path = here("Images/figure_dump"))

## check this out later! secondary axes?

# # This may useful for labelling different time scales in the same plot
# ggplot(df, aes(x = dx, y = price)) + geom_line() +
#   scale_x_datetime("Date", date_labels = "%b %d",
#   date_breaks = "6 hour",
#   sec.axis = dup_axis(name = "Time of Day",
#   labels = scales::time_format("%I %p")))
# 
# # or to transform axes for different timezones
# ggplot(df, aes(x = dx, y = price)) + geom_line() +
#   scale_x_datetime("GMT", date_labels = "%b %d %I %p",
#   sec.axis = sec_axis(~ . + 8 * 3600, name = "GMT+8",
#   labels = scales::time_format("%b %d %I %p")))


```



```{r moci and cpue}

plot1a_cpue <- blue_cpue %>%
  filter(class == "Adult") %>%
  ggplot()+
  # scale_color_manual(values = c("#666666", "#009999", "#999999" , "#000000"))+
  # scale_fill_manual(values = c("#666666", "#009999", "#999999",  "#000000"))+
  scale_color_manual(name = "Area", values = c("#666666", "#104E8B","#999999" , "#000000"))+
  scale_fill_manual(name = "Area", values = c("#666666", "#104E8B","#999999" , "#000000"))+
  geom_col(position = "dodge", stat = "identity", 
           aes(x = year, y = cpue_site, color = area, fill = area))+
  labs(y = "Catch per Angler Hour", x = "", 
       title = "Adult Blue Rockfish CPUE & MOCI Spline")+
  scale_x_continuous(limits=c(2006,2021),breaks = seq(2006, 2021, 2))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12))

plot1b_cpue <- blue_cpue %>%
  filter(class == "Juvenile") %>%
  ggplot()+
  ## giving a name here renames the legend.. wanted area to be capitolized
  scale_color_manual(name = "Area", values = c("#666666", "#104E8B","#999999" , "#000000"))+
  scale_fill_manual(name = "Area", values = c("#666666", "#104E8B","#999999" , "#000000"))+
  geom_col(position = "dodge", stat = "identity", 
           aes(x = year, y = cpue_site, color = area, fill = area))+
  labs(y = "Catch per Angler Hour", x = "", 
       title = "Juvenile Blue Rockfish CPUE & MOCI Spline")+
  scale_x_continuous(limits=c(2006,2021),breaks = seq(2006, 2021, 2))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12))

moci_central3 <- moci_central2 %>%
  filter(year %in% c(2007:2020))

moci_central4 <- moci_central3 %>%
  group_by(year) %>%
  summarise(central_mean = mean(central_ca))

plot2_moci <- ggplot() +
  #geom_col(data = moci_central3, position = position_dodge2(), 
           #aes(x = year, y = central_ca, color = pos_neg, fill = pos_neg))+
  geom_line(data = spline.moci, aes(x = x, y = y), size = 1)+
  geom_point(data = moci_central4, aes(x = year, y = central_mean), size = 2)+
  geom_hline(yintercept = 0)+
  geom_hline(yintercept = 3.97499, linetype = "dashed")+
  geom_hline(yintercept = -3.97499, linetype = "dashed")+
  scale_fill_manual(values = c( "#0066CC", "#CC0000"))+
  scale_color_manual(values = c( "#00008B", "#8B0000")) +
  scale_x_continuous(limits=c(2006,2021),breaks = seq(2006, 2021, 2))+
  scale_y_continuous(limits = c(-8, 11), breaks = seq(-8, 11, 2))+
  labs(y = "MOCI",  x = "", caption = "Data Source: http://www.faralloninstitute.org/moci")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        legend.position = "none",
        plot.caption = element_text(size = 5))

cpue_bar_moci_spline_class_a <- plot1a_cpue/plot2_moci
cpue_bar_moci_spline_class_j <- plot1b_cpue/plot2_moci


#ggsave("cpue_bar_moci_spline_class_j.png", plot = cpue_bar_moci_spline_class_j, dpi = 1000, width = 8, height = 6, path = here("Images/figure_dump"))

```


## Length Frequency
### Density plot

```{r lf density plots}

## add size cutoff for juvenile, or else leave all data in
dens_dat <- master %>%
  filter(species == "BLU", num_caught != 0) %>%
  mutate(year = as.factor(year)) %>%
  ## uncount is a super important step here. Each individual fish should be it's own line
  ## they were consolidated for CPUE calculations
  uncount(num_caught) %>%
  mutate(area = case_when(
    area == "AN" ~ "A\U00F1o Nuevo",
    area == "PL" ~ "Point Lobos",
    area == "BL" ~ "Piedras Blancas",
    area == "PB" ~ "Point Buchon"
  ))

dens_dat$area <- factor(dens_dat$area, levels = c("Point Buchon", "Piedras Blancas",
                                                  "Point Lobos", "A\U00F1o Nuevo" ))

dens_mpa_ref <- dens_dat %>%
  #filter(year == 2008) %>%
  ggplot()+
  geom_density_ridges(aes(x = size, y = area, color = site, fill = site), alpha = 0.3, 
                      show.legend = T)+
  labs(y = "", x = "Size (cm)")+
  facet_wrap(year~.)+
  theme_bw()+
  theme(panel.grid = element_blank())

dens_dat$area <- factor(dens_dat$area, levels = c("A\U00F1o Nuevo", "Point Lobos", 
                                                    "Piedras Blancas", "Point Buchon"))
dens_dat$year <- factor(dens_dat$year, levels = c(2020:2007))

dens <- ggplot()+
  geom_density_ridges(data = dens_dat, aes(x = size, y = year, fill = year), 
                      show.legend = F)+
  geom_vline(xintercept = 21, col = "red")+
  scale_fill_manual(values = c( "#000000" ,"#003399", "#0000FF", "#3366CC","#006699", "#336666",
                               "#339999","#33CCCC", "#33FFFF", "#00FFCC", 
                               "#00FF66", "#00FF33", "#009933", "#006633"))+
  labs(title = "Blue Rockfish Size Density") +
  facet_grid(site ~ area) +
  theme_bw()+
  theme(panel.grid = element_blank())

dens

#ggsave("dens_mpa_ref.png", plot = dens_mpa_ref, path = here("Images/figure_dump"), dpi = 1000, width = 8, height = 6)



```


### Bar Plots


```{r}
## Length Frequency bar plots... all, adults, and juveniles

## put back in order
dens_dat$year <- factor(dens_dat$year, levels = c(2007:2020))

# check <- dens_dat %>%
#   filter(size == 20, area == "A\U00F1o Nuevo", year == 2016) %>%
#   group_by(drift) %>%
#   count()


dens_dat %>%
  ggplot()+
  geom_bar(aes(x = size, color = site)) + 
  facet_grid(area ~ year)


```

